---
title: "Basic Transformations with WGT"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{basic-transformation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

First things first, we load up the package:

```{r setup}
library(wgt)
```

Now let's create some data to transform. We'll use a log-normal mixture: 

```{r, out.width="75%", dpi=300}
N = 500
x <- c(rnorm(N,-3/2,1/3),rnorm(N,3/2,1/3))
x <- exp(x)
hist(x,breaks=floor(sqrt(N)))
```

now we can transform it with `wgt::estiamte`

```{r}
wgt_out <- wgt::estimate(x,eta=3/4)
```

the most important arguments to `estimate` are the data itself `x` and the value for `eta` which determines how far long our geodesic we travel. Valid values for `eta` range from `0` to `1`. A reasonable starting point is `eta=3/4`. The `estimate` function returns an object with several values:

```{r}
names(wgt_out)
```

the most important is `y` which is the transformed data:

```{r}
y <- wgt_out$y
```

We can now make a plot of our data after transformation: 

```{r, out.width="75%", dpi=300}
hist(y,breaks=floor(sqrt(N)))
```

One may expteriment with different values of `eta` to get different transformations. For example `eta=1/4`

```{r, out.width="75%", dpi=300}
wgt_out <- wgt::estimate(x,eta=1/4)
y <- wgt_out$y
hist(y,breaks=floor(sqrt(N)))
```

or `eta=1/2`:

```{r, out.width="75%", dpi=300}
wgt_out <- wgt::estimate(x,eta=1/2)
y <- wgt_out$y
hist(y,breaks=floor(sqrt(N)))
```